The Anthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2023-04-14 paper.tex
update core modules

The ontology consists of the following core modules, see \cref{fig:modules}:
%For the categories, there were the following spreadsheets: bones, anatomical landmarks, osteometric landmarks, measured distances, function (separately for discriminant and regress functions), anatomical position descriptions, sources used, and osteological terminology.
\subsection{Bones}\label{sec:bone}

@@

\subsection{Teeth}
\subsection{Measurements}
Measurements consist of references to sections, the start point, midpoint, end point, and short definitions.

\todo{Umschreiben von Modulen auf ANNOdc}
\subsection{Functions}
Functions are categorized into sex determination and regress functions for body height estimation.
RDF is not optimized for mathematical formulas so we model those as literals.

>>>>

The ontology consists of the following core modules, see \cref{fig:modules}:
%For the categories, there were the following spreadsheets: bones, anatomical landmarks, osteometric landmarks, measured distances, function (separately for discriminant and regress functions), anatomical position descriptions, sources used, and osteological terminology.
\subsection{Anatomical Structures}\label{sec:bone}

@@

\subsection{Landmark Properties}

\subsection{Relative Landmark Positions}

\subsection{Landmark Line Regions and Measurements}
Measurements consist of references to sections, the start point, midpoint, end point, and short definitions.

\todo{Umschreiben von Modulen auf ANNOdc}
\subsection{Phenotypes and Functions}
Functions are categorized into sex determination and regress functions for body height estimation.
RDF is not optimized for mathematical formulas so we model those as literals.
